% THIS IS AN EXAMPLE DOCUMENT FOR VLDB 2012
% based on ACM SIGPROC-SP.TEX VERSION 2.7
% Modified by  Gerald Weber <gerald@cs.auckland.ac.nz>
% Removed the requirement to include *bbl file in here. (AhmetSacan, Sep2012)
% Fixed the equation on page 3 to prevent line overflow. (AhmetSacan, Sep2012)

\documentclass{vldb}
\usepackage{graphicx}
\usepackage{balance}
\usepackage{url}
\usepackage{times,amsmath,epsfig}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{algorithm} 
\usepackage{algorithmic}  
\usepackage[algo2e,linesnumbered]{algorithm2e} 
\usepackage{amsfonts}
\usepackage{amsbsy}
\usepackage{graphicx}
\usepackage{physics}
\usepackage{color}
\usepackage{subfigure}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{paralist}
\graphicspath{ {images/} }
\setlength{\tabcolsep}{2pt}
% \setlength{\textfloatsep}{9pt}

\newcommand{\cs}[1]{\texttt{\char`\\#1}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\f}{\mathbf{f}}
\newcommand{\Y}{\mathcal{Y}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\Set}{\mathcal{S}}
\newcommand{\Loss}{\mathcal{L}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\K}{\mathfrak{K}}
\newcommand{\x}{\mathrm{x}}
\newcommand*\Bell{\ensuremath{\boldsymbol\ell}}


% Include information below and uncomment for camera ready
\vldbTitle{Data Synthesis based on Generative Adversarial Networks}
\vldbAuthors{Noseong Park, Mahmoud Mohammadi, Kshitij Gorde, Sushil Jajodia}
\vldbDOI{https://doi.org/TBD}

\begin{document}

% ****************** TITLE ****************************************

\title{Data Synthesis based on Generative Adversarial Networks}


% possible, but not really needed or used for PVLDB:
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as\textit{Author's Guide to Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and BibTeX} at \texttt{www.acm.org/eaddress.htm}}}

% ****************** AUTHORS **************************************

% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{2} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.

\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Noseong Park, Mahmoud Mohammadi, Kshitij Gorde\\
       \affaddr{University of North Carolina}\\
       \affaddr{Charlotte, North Carolina, USA}\\
       \email{\{npark2, mmoham12, kgorde\}@uncc.edu}
% 2nd. author
\alignauthor
Sushil Jajodia\\
       \affaddr{George Mason University}\\
       \affaddr{Fairfax, Virginia, USA}\\
       \email{jajodia@gmu.edu}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
% \additionalauthors{Additional authors: John Smith (The Th{\o}rv\"{a}ld Group, {\texttt{jsmith@affiliation.org}}), Julius P.~Kumquat
% (The \raggedright{Kumquat} Consortium, {\small \texttt{jpkumquat@consortium.net}}), and Ahmet Sacan (Drexel University, {\small \texttt{ahmetdevel@gmail.com}})}
\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.


\maketitle

\begin{abstract}
Privacy is an important concern for our society where sharing data with partners or releasing data to the
public is a frequent occurrence. Some of the techniques that are being used to achieve privacy are to remove
identifiers, alter quasi-identifiers, and perturb values. Unfortunately, these approaches suffer from two
limitations. First, it has been shown that private information can still be leaked if attackers possess
some background knowledge or other information sources. Second, they do not take into account the
adverse impact these methods will have on the utility of the released data.

In this paper, we propose a method that meets both requirements. Our method, called \textit{table-GAN}, uses generative adversarial networks (GANs) to synthesize fake tables that are statistically similar to the original table yet do not incur information leakage.

We show that the machine learning models trained using our synthetic tables exhibit performance that
is similar to that of models trained using the original table for unknown testing cases. We call this
property \textit{model compatibility}. We believe that anonymization/perturbation/synthesis methods
without model compatibility are of little value.

We used four real-world datasets from four
different domains for our experiments and conducted in-depth comparisons with state-of- the-art
anonymization\slash perturbation\slash generation techniques. Throughout our experiments, only our method consistently shows balance between privacy level and model compatibility.
\end{abstract}

\input{sections/intro.tex}
\input{sections/related.tex}
\input{sections/motivation.tex}
\input{sections/method.tex}
\input{sections/experiments.tex}

% \section{Final Remarks and Future Work}
% Existing anonymization methods show good model compatibility (except the classification tests in the Health and LACity datasets). However, their privacy level is weaker than table-GAN, as shown in the DCR tests.

% Our table-GAN shows very stable model compatibility in all datasets and its privacy level is much higher than other baseline methods. We will extend our method to process all data types of relation databases.
\section{Conclusion}

We proposed a method called table-GAN to synthesize tables. Our method shows as good model compatibility as anonymization techniques that do not change sensitive attributes. To our knowledge, our method is the first attempt to synthesize general relational databases using deep learning techniques.

We performed experiments using four real-world datasets with millions of records and tens of attributes. The runtime to synthesize such large databases is approximately 20 minutes with our entry-level servers due to the advancements in GPU technology. In the statistical, distance to the closest record, and model compatibility tests, table-GAN exhibits the best trade-off between privacy level and model compatibility.

In the future, we plan to extend our method to other data types such as strings and further improve the generation quality. We hypothesize that data synthesis based on well-designed generative models can lead to perfect model compatibility.

\clearpage
\bibliographystyle{abbrv}
\bibliography{gan,Zotero}  % vldb_sample.bib is the name of 



\end{document}
